% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,twoside,twocolumn,openany,nodeprecatedcode,
  letterpaper,bg=full]{dndbook}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\newfontfamily\gillius{GilliusADFNo2}[NFSSFamily=GilliusADFNoTwo-LF]
\sloppy
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\chapter{Dungeons \& Gardens}\label{dungeons-gardens}

\DndDropCapLine{T}{he salt spray stings your faces} as the longship
grinds against the icy pier of Palebank Village. The groan of
splintering ice mixes with the cries of gulls and the shouts of
dockworkers bundled in furs. Palebank Villages greets you with a blast
of frigid air, a stark contrast to the relative warmth of the southern
seas you've left behind. The sky above is a perpetual grey, heavy with
the promise of more snow.

You've endured weeks at sea, braving treacherous currents and icy
squalls aboard the \emph{Frostwind}, a sturdy, if somewhat cramped,
longship captained by the weathered and taciturn Jarl Stonebeard. The
journey itself proved more than just a test of sea legs; it was during
those long, monotonous days and nights that your paths first crossed.
Over shared meals of salted fish and hardtack, huddled around the meager
warmth of the ship's brazier, you discovered a shared purpose beneath
your disparate backgrounds. Perhaps it was a whispered conversation
overheard in the galley, a chance encounter on deck under the pale
moonlight, or a late-night debate in the cramped crew quarters, but you
each realized you were drawn north by the same alluring whispers: the
rediscovery of Aeorian ruins, remnants of a lost civilization swallowed
by the Frostfell. Tales of lost cities and powerful artifacts have
spread like wildfire, carried on the winds and traded in taverns from
the Menagerie Coast to the shores of Wildemount. These stories have
lured explorers, scholars, and fortune-seekers alike to this desolate
land, and fate, or perhaps something more, has brought you together on
this shared voyage.

Palebank Village, a ramshackle collection of wooden buildings huddled
against the harsh landscape, serves as the primary gateway to the frozen
Island of Eiselcross to the North. Here, amidst the bustle of fur
traders, fisherfolk, grizzled explorers, shady mercenaries and hopeful
fortune-seekers, you disembark. The air is thick with anticipation, a
palpable sense of excitement mixed with a healthy dose of apprehension.
The promise of uncovering lost knowledge, powerful magic, and perhaps
even unimaginable wealth hangs heavy in the air, a beacon in this frozen
wilderness. But the frozen shores of Eiselcross hold many secrets, and
the ruins of Aeor are guarded by more than just ice and snow. Ancient
dangers stir beneath the frozen surface, and the secrets you seek may
come at a terrible price. Your journey into the heart of Eiselcross
begins now, the moment your boots touch the frozen ground.

\chapter{Welcome to Palebank Village}\label{welcome-to-palebank-village}

\DndDropCapLine{I}{n the frosty expanse of the} colder reaches of
Wildemount, in the Greying Wildlands south of the Islands of Eiselcross,
lay the haphazard cluster known as Palebank Village. It was a place more
cobbled together than planned, with just over a hundred cabins and
shacks pressed against the northern cliffs that rose a mere fifteen feet
against the lapping rhythms of the icy harbor waves. The docks, busy
with the absence of departing ships, whispered tales of neglect and
wariness.

On this frigid day, the village was subdued, gathered in mournful
procession for the unfortunate Urgon, a dwarven adventurer whose final
journey was to the graveyard west of the harbor. There, encased in a
casket more suitable for a relic than a beloved friend, he lay suspended
in a state of frozen eternity. Villagers whispered tales of his return
from a year-long venture into Eiselcross, burdened with treasures and a
chilling affliction. Despite countless efforts, Urgon could never find
warmth. Eventually, blue streaks marred his pallor, snaking through his
veins, until his entire being succumbed to the grip of frost.

We followed the procession, taking note of the landscape dotted with
quaint inns and supply shops. Amongst the mourners stood a weathered elf
adorned with the insignia of a ``Glassblade''. Introducing himself as
Elro, he shared that the usual voyages to Aeor had ceased; a silent
testament to the mystery shrouding Urgon's demise. Elro sought our help
in unveiling the source of this insidious curse, admitting that Urgon's
home remained unexplored.

Word reached us quickly that another villager named Tulgi was showing
similar symptoms---her fate seemingly entwined with Urgon's.
Fortuitously, their cabins stood in proximity.

\section{Beer with the Locals}\label{beer-with-the-locals}

In the heart of the village, a jovial dwarf Bortock tended bar at the
local tavern. Elara, ever inquisitive, engaged Bortock in conversation
about Urgon's recent exploits. A night's rest was negotiated---two rooms
for eight silver pieces---before being served beer by the bucket and a
meal of squid rolls.

Bill, a stalwart Glassblade at one of the tavern tables, emphasized that
due to the danger of the curse, all boats were being warned off from
Palebank's docks. Meanwhile, we learned Tulgi was a solitary trapper,
her life a mystery to most.

\section{The Cabins of Urgon and
Tulgi}\label{the-cabins-of-urgon-and-tulgi}

With this knowledge, we ventured to Urgon's cabin where another Glass
Blade vigilantly stood post. Halite led us inside, where chaos had left
its mark. The mounted head of a snowy beast with grey horns seemed to
have overseen the search. Books were strewn about, gear tossed aside as
if someone had been desperately seeking something. Scarlet's keen eyes
caught sight of a grappling hook, swiftly claiming it. Meanwhile, with a
sharp mind for details, Halite, discovered a receipt within a book.
Dated two months prior, it recorded the sale of Aeorian items at the
local Pelc's Curiosities for a handsome sum of one thousand gold pieces.
Among the items: a dagger, a scroll case, a jade statue, a quiver of
arrows, a jasper-set silver ring, and two blue glass vials.

Our eyes traced tracks leading to Tulgi Lutan's snow-burdened cabin. The
warmth of a fierce fire belied the untouched exterior and shuttered
windows. Scarlet's knock brought a curt response, followed by Elara's
soft words which coaxed the door open. Tulgi's face, marked by the same
blue streaks that had doomed Urgon, was a testament to her shared
affliction. She admitted her illness, confessing she and her sister
Hulil, newcomers from Shady Creek Run, were in league with a crime
syndicate. They had been sent to pilfer Aeorian treasures. It was they
who had ransacked Urgon's home, and Tulgi who now surrendered a finely
wrought dagger into Kragor's keeping.

She said that her sister Hulil held the remainder of the treasures in
Croaker Cave, though Tulgi hadn't seen her in weeks.

\section{Onward}\label{onward}

With our next destination clear, we hiked to Pelc's Curiosities. We
found the shop marked by a dragon-gilded ``P'' where the front door
sagged invitingly open, beckoning us into the next chapter of this
unfolding tale.

\chapter{Pelc's Curiosities}\label{pelcs-curiosities}

\DndDropCapLine{T}{he party stands outside Pelc’s} Curiosities, the door
slightly ajar. Suspecting intruders, Whisper closes her eyes while
softly purring ``Maior et Fortior''. The air around her shimmers
momentarily as she draws on her inner ki in concentration. She then
peers into the doors and the windows of the building. Despite her
efforts, she cannot make out very much, though she hears enough rustling
to make her hairs bristle. It sounds as though there are several inside
ransacking the place. Scarlet joins Whisper's investigation, attempting
to divine whether the noises might simply be animals, yet she senses no
wildlife inside.

Preparing for potential conflict, Kragor stands up straight and
stretches out his arms as if to grasp a weapon. In a loud yet distant
voice he exclaims ``Malleum Evoco''. Suddenly ethereal shadows stream in
from all directions and coalesce into an obsidian black war hammer with
an angular and brutal head. Its every surface is etched with subtle
twisting runes. Kragor hefts the weapon with both hands, then widens his
stance with feet planted firmly on the ground.

The goliath Halite likewise readies himself, his massive frame towering
above even Kragor. With deliberate, practiced movements, he adjusts his
gleaming bronze shield, its surface etched with intricate clan markings.
In one enormous hand he carefully grips his trident, its three wickedly
barbed prongs designed not just to pierce, but to tear and rend flesh.
The trident promises not just death, but a savage, lingering demise.

\section{Surprise}\label{surprise}

Inside Pelc's Curiosities lie the answers to the freezing curse. Anxious
for action, Elara takes a deep breath, tapping into her well of magic.
Her fingers trace the air, summoning the rhythm of a battle drum. Her
magic ignites, sending an illusory racket echoing from within the shop's
shadowed walls. Startled into silence, the adversaries within hold their
breath, their schemes momentarily unraveled. As Whisper crouches beside
her, he senses the tension mounting. Without warning, a crossbow bolt
whistles past, narrowly missing him. Elara's calculated ruse works,
urging their foes to react blindly. The door slams shut, a temporary
barrier between them and danger.

``So much for the element of surprise,'' mutters Kragor.

Undeterred, Elara shoulders the door open again. Darkness seeped around
her like ink in water, yet her keen eyes, accustomed to shadow,
discerned the outlines of two startled bandits amid the cluttered ruins
of the shop. Ancient relics lay strewn about like casualties of an
invisible war; toppled bookshelves and shattered relics spoke of a
hasty, chaotic search.

The bandits, their nerves frayed by Elara's eerie magic, released their
crossbow bolts in a jittery frenzy. The bolts missed their marks,
striking harmlessly against worn brick and aged wood. Assessing the
chaotic tableau before her, Elara hesitated; caution whispered in her
ear, suggesting a withdrawal from direct assault into strategic retreat.

\section{Inspiration and Fog}\label{inspiration-and-fog}

She retreated to her waiting comrades, her mind spinning a fresh
tapestry of strategy. Checking again her surroundings, Kragor meets her
gaze with a blend of curiosity and gruff admiration. Her eyes locked
with his, and in that silent exchange, understanding was born. Elara
struck her hand drum, each beat a pulse of power transmitted through the
air, wrapping around Kragor like a cloak of inspiration. The rhythmic
symphony reignited his focus, sharpening his spirit for the clash ahead.

But as this is happening, Scarlet quickly reacts. ``Voco Nubes!'' she
bellows while raising her gnarled staff to the sky. Her eyes close in
concentration as she summons nature's veil. Wisps of mist curl around
her fingers before surging toward the building. The vapor seeps through
cracks and under doorways, expanding rapidly into a dense, swirling fog
that blankets the room. The once-clear space becomes an opaque, ethereal
haze, obscuring vision and muffling sound. The druid smiles, knowing the
shrouded interior will confound any occupants, granting her allies the
advantage they seek within the murky cover of the fog cloud. She wastes
no time taking advantage of it herself: she sneaks into the building and
hugs the wall, moving to the right. She can hear others moving inside as
well, but can make out nothing through the fog.

\section{First Blood}\label{first-blood}

Watching one of his allies attacked and another diving into the fog and
what must certainly be mortal danger, Kragor strains to think. He feels
like a sitting duck outside with obscured enemies inside, ready to make
a pincushion out of him with their crossbow bolts. Taking a deep breath
to overcome his fear, he too rushes through the doorway into the
shrouding fog, gripping his massive conjured war hammer tightly. Unable
to see, he positions himself protectively before where he believes
Scarlet to be, straining to detect any threats hidden in the mist. A
sudden noise to his left spurs him into action. He swings wildly, the
war hammer arcing through the air, and feels a heavy impact followed by
a muffled crunch. The enemy's body collapses to the ground with a
lifeless thud.

\section{The Roof}\label{the-roof}

Outside, Whisper's sharp tabaxi senses are attuned to every movement
around her. As her gaze sweeps upward, it catches upon an unexpected
anomaly: a crouched form perched on the rooftop. Though the figure's
features are obscured by distance, their posture is a tapestry of
uncertainty, a riddle waiting to be unraveled. Without hesitation,
Whisper draws upon her innate agility, launching herself up the
building's facade, her movements a dance of precision and power. Within
moments, she alights upon the roof beside the puzzled figure. As she
closes in, a momentary clumsiness intrudes upon her fluid motion; her
limbs entangle with the figure in a grapple that is awkward but
surprisingly effective. Despite the ungraceful tangle of arms and legs,
her determination holds fast, securing her quarry beneath the vast blue
sky. The figure, now clearly a rogue based on their dark attire and
tools of the trade hanging from their belt, desperately attempts to free
themselves from Whisper's grasp, to no effect.

\section{Counterattack}\label{counterattack}

Halite now grasps the perilous choice the party has made in their
recklessness. With a fierce resolve etched in the hard lines of his
goliath visage, he charges through the fog-choked doorway, instinctively
veering left to secure the flank opposite Scarlet and Kragor. The mist
clings to him, a shroud of uncertainty, yet he moves with the confidence
of one accustomed to the unseen. A bandit lunges at him, the attack a
mere whisper of danger that dissolves into emptiness. Seizing the
opportunity, Halite's fingers tighten around his trident, that harbinger
of despair. With an expert thrust, the weapon slices through the fog,
hungry for blood. It strikes true, embedding itself deep within the
bandit with a sickening resistance, as though the weapon savored its
work. Halite has to struggle to wrench it free from the bandit with raw
power, the action accompanied by a dreadful noise that the fog quickly
absorbs.

While recovering his favored weapon, Halite hears the ``whoosh'' of a
crossbow bolt. He flinches, but he is not the target. He hears Kragor
cry out in desperate pain.

The bolt had struck Kragor just below the collarbone, close to his
heart. Blood flows unchecked, staining his leather armor.

Seconds later, another bolt pierces Scarlet and a sharp pain flares
beneath her ribs. Blood seeps into her cloak, mingling with the forest's
earthy scent.

\section{Rogue Fall}\label{rogue-fall}

Whisper, poised at the edge of the rooftop's precipice, maintains a firm
hold on the rogue. Despite the rogue's cunning and agility, he struggles
to free an arm to launch a counterattack with his dagger. Nevertheless,
Whisper's sharp claws and expert grip keep him securely restrained.
Beneath her, the store's chaos swirls, a symphony of survival and
sorcery; each cry, each clash a note struck sharp in the chord of battle
below. Her decision solidifies with the clarity of ice forming,
abandoning subtlety for swiftness. With a sudden, fluid ferocity, she
thrusts the entangled rogue from the roof, the figure plummeting and
landing with a sickening thud upon the hard earth. The world contracts
around her as she vaults down, feline grace reclaiming momentum in
mid-air, her heart a steady drumbeat beneath her silken fur. She lands
silently, flowing through the doorway like a stream of midnight water
into the tempest of friend and foe, ready once more to thread her
prowess into the weaving of combat's fierce tapestry. The thrown rogue,
battered and broken, lies forgotten amidst the rubble.

Elara is startled by Whisper's sudden reappearance. Despite this, she
remains focused on the building, her senses registering enough to grasp
that her companions are in grave danger. She urgently calls out to
Scarlet, telling her to dispel the fog cloud, which Scarlet promptly
does. Without hesitation, Elara rushes to join her and Kragor inside.
Whisper follows but pauses in the doorway, alert for threats inside or
out.

\section{Medic!}\label{medic}

Surveying Scarlet and Kragor's injuries, she quickly assesses that
Kragor's condition is more critical. She places her hands gently on the
grievous puncture wound left by the crossbow bolt, her touch glowing
with divine energy. The healing light rapidly closes the wound,
restoring vitality to his mottled green-gray skin. Kragor, caught off
guard yet deeply appreciative, meets Elara's kind gaze, and a silent
bond is forged between the orc and the aasimar.

\section{Final Blows}\label{final-blows}

As Elara is tending to Kragor, Scarlet runs towards a nearby bandit that
is just now orienting themselves after the fog dispersed. Eyes glowing
with untamed magic, Scarlet calls upon nature's wrath. With a fierce,
primal incantation, her fingertips elongate into razor-sharp claws,
dripping with corrosive acid. In a swift motion, she lashes out, and her
savage strike lands true. The bandit staggers back, pain etched across
their face as the toxic claws rend through leather and flesh, leaving a
searing wound. The druid's usually gentle demeanor is momentarily
overshadowed by raw, feral power, as the bandit teeters on the brink of
defeat, humbled by nature's unforgiving might.

Halite steps forward with a grim determination, his massive form casting
a foreboding shadow over the bandit struggling to stay upright from
Scarlet's fierce attack. With a swift and fluid motion defying his
immense size, Halite shifts his weight back, then lunges forward with an
uppercut trajectory. It pierces through the air with a whistling sound,
meeting the bandit's chest in a visceral collision. The force of the jab
lifts the bandit off his feet momentarily, his final gasp cut short by
the weapon's deadly embrace. Life flickers out of his eyes, and the limp
body slides down the trident's length. Halite grimaces, more out of
reflex than malice, as he shakes the bandit free with a swift, practiced
motion, the lifeless form dropping to the ground with a thud.

Now sufficiently recovered to rejoin the battle, Kragor focuses his
attention on the bandit far across the room that he suspects of shooting
him. Although he can't be sure of the bandit's guilt, he raises his war
hammer toward his target and shouts, ``Te Exsecro!'' The air shimmers
with malevolent energy as a cold, dark aura coils around the bandit like
an invisible serpent. Without hesitation, Kragor follows with another
spell, yelling ``Dolor,'' and unleashes a surge of eldritch energy from
his war hammer that strikes the bandit square in the chest. The impact
of the blast results in an ugly wound. Immediately, shadowy tendrils
twist and curl over the shredded flesh causing it to blacken and
crumble, leaving the bandit teetering on the brink of death.

\section{Surrender}\label{surrender}

Halite, his towering form casting an imposing shadow across the
cluttered interior of the ransacked antique shop, moved with purpose
toward Kragor's target: a bandit whose bravado had been seared away by
the crackling energy of the orc warlock's magic. The air still shimmered
with the fading traces of arcane power, and the bandit, already on the
brink of collapse, could only watch as the goliath fighter closed the
distance between them like an inexorable force of nature.

The trident in Halite's grip gleamed with an unsettling menace, its
barbed points promising a swift and painful end should it be called upon
to deliver one. The bandit, a mere lithe elf in the presence of such
formidable warriors, felt the weight of his own mortality for what
seemed like the first time. His sword clattered to the wooden floor, a
hollow sound that resonated through the shop, punctuating his surrender.

``I yield,'' the bandit croaked, his voice strained with fear and
desperation. He raised his hands, palms open and empty, a universal sign
of capitulation. His eyes darted to his remaining comrade, wide with
silent urging.

The last standing bandit, who had watched the battle unfold with growing
dread, knew the odds all too well. He had witnessed the fate of their
fallen companions---three already dispatched with ruthless efficiency by
the duo of Kragor and Halite. The decision was not a difficult one.

He dropped his own weapon, a well-worn crossbow, to the floor and raised
his hands above his head in submission. ``We don't want anymore
trouble,'' he said, his voice carrying a tremor that matched the frantic
beating of his heart.

Kragor surveyed the scene, his eyes, glowing faintly with residual
magical energy, meeting Halite's. An unspoken understanding passed
between them---this victory, as hard-fought as it was, did not need to
claim further lives.

With the tension of combat beginning to ebb, the antique shop's air felt
still, though the echoes of the skirmish lingered. Surrounded by
overturned furniture and scattered relics of a bygone era, the bandits'
surrender marked the end of the struggle, their lives spared by the
mercy of those far mightier than they.

Whisper, having ensured the rogue she tossed from the roof was no longer
a threat, finally entered the antique shop and closed the door behind
her. As she did, the rogue moved to a crouched position around the
corner, relieved that his theatrics had been successful. Intending to
enter the building when the coast was truly clear, he remained vigilant,
pressing his ear to the cool glass of the window to eavesdrop on the
victorious adventurers.

\section{Interrogation}\label{interrogation}

Elara and Scarlet eyed the bandits with intensity, their curiosity
piqued by the confession of surrender. ``Who are you and what were you
doing here?'' Elara demanded, her voice steady yet demanding answers.

The first bandit, regaining a bit of composure but still visibly shaken,
replied, ``We were sent by Hulil, a priestess of Tiamat. She instructed
us to search this place. Two months ago, there was a robbery here, and
now Hulil's got this strange freezing sickness. She hoped we might find
a clue here in the shop. But we found nothing.''

Scarlet's gaze remained firm as she pressed further, ``Then why did you
attack us?''

A hint of embarrassment colored the bandit's cheeks. ``We were spooked.
We heard some weird noise, then you guys barged in. Especially that
chick with a horn on her head,'' he gestured toward Elara. ``We
panicked. We're not used to dealing with people like you.''

In the meantime, the rogue outside, crouching below the window, absorbed
the exchange, piecing together the dynamics at play.

Scarlet produced a weathered receipt with notations about Aeorian
artifacts and presented it to the bandits. ``Have you seen these
items?''

``They're with Hulil,'' the bandit admitted reluctantly, his eyes on the
documentation with evident recognition. ``She's at Croaker's Cave,''
confirming what the party had already learned from Hulil's sister,
Tulgi.

Satisfied with the information, Kragor dismissed the subdued bandits in
no uncertain terms: ``Leave everything and get out.'' Seizing their
chance, the bandits quickly discarded their weapons and coins before
hurrying for the door, the rogue outside remaining concealed until the
coast was truly clear.

\section{Loot}\label{loot}

After searching the bandits' leavings and their late compatriots'
bodies, the party tallied the loot: 14 gold pieces, eight silver pieces,
five crossbows, 30 bolts, five scimitars, and a dwarf-sized shirt
blazoned with ``Scanlan Shorthalt --- The Meat Man Cometh''. (Elara
judged this last item to be a rare find and might fetch as much as two
gold pieces.)

The party then turned to the antique shop, assessing the chaos that
engulfed it. The room was in disarray, bookshelves overturned and
trinkets strewn about. Amidst the disorder, they stumbled upon a
chilling sight---a frozen elf lying lifeless in bed. It was Verla Pelc,
and the grim discovery confirmed that the place had not seen tidiness
for weeks.

In a thorough inspection of both the shop and the dead bandits'
belongings, they discovered two bows and various odds and ends. Deciding
a respite was in order, they planned to rest before heading to Croaker
Cave.

\section{Who is this guy?}\label{who-is-this-guy}

Unbeknownst to the adventurers, the rogue remained vigilant, listening
to their intentions and preparing to bide his time until they left.

\chapter{Secrets of Croaker Cave}\label{secrets-of-croaker-cave}

\DndDropCapLine{T}{he party retraces their steps} to the \emph{Jolly
Dwarf}, where warmth greets them like an old friend. As the tavern's
door swings open, hearth light flickers along the walls, merging with
murmurs and the clinking of mugs. After a day of skirmishes, they retire
to modest rooms, voices still echoing with plans.

Morning in Palebank Village dawns with a crisp, biting air. Frost clings
to windows, and the adventurers rise at half-past seven. Below, a kettle
hisses, and the aroma of breakfast fills the inn. Unusually quiet due to
the port's closure, the inn has only one family--- a weary pair of men
with twin tiefling girls--- depart, the door framing their retreat in
the morning light.

Bortock, the innkeeper, greets them cheerily. ``Elro was around last
night, looking for you lot,'' he says, ``He'll be back soon for news.''

As Halite asks about Croaker Cave, Bortock's expression shifts subtly to
one of caution. ``Croaker Cave, you say? They call it that for good
reason--- the croaks of giant ice frogs echo from there, a sound that'd
chill your bones if the cold hadn't already. None of the village folk
dare set foot inside. They know where to find it, sure, but it's an
unspoken rule here: no one goes into that cave.''

Taking a seat, the party enjoys breakfast--- warm bread, stew, and fish;
a bargain at only five silver pieces--- while Kragor inquires about
Hulil, Tulgi's sister. Bortock scratches his beard thoughtfully, his
eyes narrowing as he sifts through what bits of information he
possesses. ``Ah, Tulgi,'' he begins slowly, weighing his words. ``Can't
say I knew she has a sister. These folks from Shadycreek Run--- always a
tangled web with them. Their kin aren't exactly welcome in Palebank.
Suspicion tends to follow their kind.''

Ever the pragmatic, Kragor poses another question: ``What about healing
potions? Do you know where we might procure some?''

Bortock advises, ``Try the docks. There's an old elf woman, Gramini, she
sells them. Pricey, but worth it.''

As breakfast concludes, Elro joins them, concern in his eyes. Scarlet
updates him on their findings: connections between Tulgi, Hulil, and the
village's affliction, and the tragic fate of Verla from Pelc's
Curiosities. Elro nods, confirming suspicions about the Shadycreek Run
families. News of dispatched bandits lightens his demeanor. ``Less to
worry about,'' he says, intending to send his men over to shop to clean
up.

Still curious about their next venture, Whisper inquires, ``What makes
Croaker Cave particularly dangerous?'' Elro turns towards her, his gaze
steady. ``It's the giant ice frogs. Those are the reason folks steer
clear.''

Scarlet, drawing from her vast trove of natural knowledge, leans
forward. ``How large are these frogs?'' she asks.

``About the size of a large wolf,'' Elro replies, conjuring a vivid
image in their minds.

Scarlet nods, familiar with their temperate climate counterparts. She
addresses the party. ``I recall they aren't venomous, but they can
certainly swallow a person whole. Their stomach acid dissolves their
prey, and while they're smarter than regular frogs, they're not what you
would call cunning. I knew a teacher once who kept one as a pet.''

Before departing, Elro implores, ``Root out those Shadycreek folks. The
village would owe you greatly.''

The party, girded by Elro's trust and responsibility, reflects on the
tapestry they are unraveling--- a tapestry that now leads them to the
hidden depths of Croaker Cave and the shadows lurking within.

\section{Adventuring is hard, let's go
shopping}\label{adventuring-is-hard-lets-go-shopping}

Braving the biting cold, our adventurers reach the docks--- a sprawling
network of paths and shanties, each whispering tales of a bygone era.
They navigate these lanes, finding the shack they seek: a dilapidated
structure with an askew ``Goods for Sale'' sign dangling overhead.

Elara steps forward as the negotiator. Halite opens the door, releasing
the tinny clang of a bell. Inside, flickering firelight reveals shelves
groaning under the weight of indescribable trinkets. Behind the counter
emerges a wizened elf whose blue scarf and loose coat defy the chill
that seeps through the shack's walls. Her eyes, sharp despite her age,
study the newcomers with cautious curiosity.

``Well, well, what's this? Adventurers, by the look of you.'' Her voice,
both raspy and warm, mirrors the fire's flicker. ``What brings you here?
Looking for trinkets, or is it something more substantial?''

Elara approaches, broaching the need for potions. ``You must be Gramini.
We seek anything to combat the freezing illness cursing this village.''

The woman's expression shifts, a glint of sympathy mixing with
practicality. ``Ah, if you mean Urgon's ailment, that mystery is beyond
my humble potions. But I have supplies for those brave enough to venture
to Eiselcross. Dangerous place, that is.''

She presents four health potions. ``Usually 60 gold apiece, but business
has been slow lately. I'll sell them for 50 each.''

Seeing an opening, Elara leans in. ``Could you let them go for 30 each?
The road ahead is perilous.''

Gramini chuckles, a sound steeped in kindness and shrewdness. ``Below
cost, Sweetie? But you've got charm, I'll give you that. Alright, 48
each. A gesture of goodwill.''

The negotiation leaves Elara hopeful. With business nearing conclusion,
curiosity tickles her again. ``Heard any tales or warnings of late,
Gramini?''

Leaning back, the old elf sighs. ``Troubling times, indeed. The port's
closed--- no ships. Palebank seems to hold its breath, waiting for a
storm to pass.'' Her voice drops to a whisper, eyes locking with
Elara's. ``That freezing disease, eating at the core. Aeor is where its
dark magic likely thrives. Everything from that land carries a cost,
mark my words.''

Elara then suggests, ``We're short on coin\ldots{} Perhaps a barter?''

Kragor, catching on, brandishes a shirt emblazoned with the name Scanlan
Shorthalt. Gramini's eyes gleam with recognition. ``Him! I've seen him
perform.'' Fond remembrance softens her demeanor.

She proposes, ``I'll give you 15 gold off the potions for that.''

Donning the bard's shirt with delight, Gramini is transformed into a
giddy teenager for a few moments. ``Scanlan was so charming!'' Her
laughter chimes like a song, sealing the deal.

As the party exits, spirits buoyed, Gramini's unexpected joy lingers, a
beacon against the looming shadows.

\section{Doctor Pepe}\label{doctor-pepe}

As the party approaches Croaker Cave, they note smoke spiraling upward
from a natural chimney, etching the sky with its ashen tendrils. Despite
the spectral warning, the front opening of the cave appears unguarded.

Unbeknownst to them, the rogue that Whisper had previously encountered
lies in wait, having shadowed the party from Palebank. As they draw
nearer, he steps free of the forest's embrace, his presence a sudden
ripple in the serene tableau.

``Hail, Friends! I mean you no harm,'' he calls out, raising his hands
in a gesture of peace. ``I have something I believe you need to know.''

Scarlet and Whisper exchange glances before fixing their gazes upon the
rogue. Recognition flickers in Whisper's eyes, a soft chuckle escaping
her lips as she recalls their prior exchange on the rooftops of Pelc's
Curiosities. Scarlet's expression is more guarded as she steps forward,
her tone firm yet open. ``Who are you?'' she demands, her eyes narrowing
with a blend of caution and curiosity. ``And what do you want?''

The rogue spreads his arms in a gesture of openness. ``Let me introduce
myself. I am called Doctor Pepe,'' he announces. ``I assure you, I was
not a party to the bandits you encountered before. Like you, I've been
drawn into the orbit of this mystery, investigating the source of this
debilitating disease afflicting the village.''

Kragor steps forward, his bearing equal parts caution and curiosity.
``Well met, Doctor Pepe. What do you know of this cave?''

``Just before daybreak, I witnessed three cloaked figures enter the
cave--- a dwarf and two elves, if I'm not mistaken.'' Doctor Pepe's
eyes, sharp and perceptive, scan the adventurers' faces, gauging their
reaction. ``Whatever transpires within, it may well relate to the
affliction that has beset Palebank.''

The party exchanges thoughtful glances. After weighing their options,
the adventurers come to a shared conclusion. Offering the rouge a nod of
acceptance, Kragor extends the group's unspoken consensus. ``Then let us
consider you an ally, Doctor Pepe. Together, we may better contend with
whatever lies within the heart of Croaker Cave.''

\section{Trepidation's threshold}\label{trepidations-threshold}

As the party assesses the scene at the cave entrance, Elara's sharp eyes
catch sight of myriad footprints--- heavy and light, large and small---
tracing paths both in and out of the cavern's yawning mouth.

Gathering in a tight circle, they weigh their options and decide on a
reconnaissance mission. It is swiftly determined that Doctor Pepe, with
his keen investigative insights, and Whisper, with her silent grace,
will venture in to scout the darkness and report back to the group.

To aid them in the shadowy depths, Elara steps forward and gently strums
her harp, weaving magic through its strings. She sings, ``Sol
invictus,'' and with her melody, a spare dagger that Doctor Pepe holds
aloft begins to glow. The light emanating from the blade now serves as
both a beacon and a ward against the shadows lurking within the cave.

As Doctor Pepe and Whisper step cautiously into the cave, the world
narrows around them to the soft glow of magical light. The air grows
cooler, the dampness clinging to their skin like an insistent whisper.
About ten feet in, they encounter a pool of water, its murky depths
disturbed only by the occasional ripple from droplets falling from
above.

Whisper, pausing to scan the area, notes that the ceiling, though ten
feet high, bristles with stalactites, reducing the navigable space to
eight feet. The constant drip of water echoes in the chamber, joined
intermittently by the deep croaks of unseen amphibians. These sounds
seem to resonate with the very bones of the cave, sending a shiver
across her fur.

Doctor Pepe, moving with deliberate quiet, approaches the pool's edge to
gain a better vantage. He squints across the still water, and on the far
side, he discerns the tip of a wooden beam jutting slightly from the
shadows. Suddenly he recalls that the three figures he saw entering the
cave earlier were carrying a beam: this must be the way across.

\section{Ambush}\label{ambush}

Whisper's usual grace falters when she hits a jagged stalagmite,
unleashing a sharp hiss that pierces the cave's silence. Instantly, the
murky pool erupts, and two mastiff-sized blue frogs emerge, their slick
bodies glinting ominously.

One frog leaps at Doctor Pepe, its jaw snapping with ferocious hunger.
His reflexes, sharp from experience, save him; he sidesteps as its maw
closes on empty air. But the second frog's attention locks onto Whisper.
With a sudden lurch, it fastens its jaws around her, seriously wounding
her. Its coarse tongue feels rough against her fur as it pins her with a
vice-like grip. Whisper's world constricts around the raw strength of
the creature, her body momentarily immobilized by the force of its bite.

Her once luxurious fur matted with blood and frost, her breath shallow
and labored, Whisper summons her inner strength to claw free, leaving
shallow crimson trails across the frog's blue skin in retaliation.

Outside, Elara leads the party at the cave entrance. ``They're in
trouble,'' she asserts, urgency lacing her voice. ``We need to move!''

Within, the rhythmic echo of boots suggests more danger is approaching,
but out of necessity, Doctor Pepe and Whisper remain focused on the
immediate threat. Doctor Pepe turns his attention to the wounded frog.
His shortsword pierces its slick flesh, and his dagger follows, sinking
deep into its massive head. The creature shudders, momentarily stunned.

Recovering quickly, the frog snaps at Doctor Pepe, its powerful jaws
gripping him tightly. He grunts in pain, fighting against its hold.

Meanwhile, the first frog retreats toward the water, and Whisper's
retaliatory strike misses. Frustrated yet determined, she attempts to
help Doctor Pepe, her claws slashing his assailant and drawing blood.
Realizing she can't endure another attack, she makes a calculated
retreat, slipping gracefully back to the cave's entrance, trusting that
Doctor Pepe can handle the encroaching threat momentarily.

\section{Reinforcements}\label{reinforcements}

As Whisper emerges from the cave, Halite quickly gauges the peril, his
resolve igniting. With swift strides, he charges inside, his trident a
formidable comfort.

He finds Doctor Pepe still struggling against the frog's relentless
grip. Halite drives his trident into the creature's side, but its hold
does not falter. Observing the struggle, Elara weaves a melody with her
harp, instilling Pepe with courage. ``Remember your agility and
cunning!'' she calls, the sound of her voice and the vibrations of her
harp soothing. She then summons the power of the stars, launching a mote
of radiant energy with precision. The frog releases a guttural croak,
convulsing under the assault before it releases Doctor Pepe and
collapses lifelessly into the pool.

Grateful and relieved, Doctor Pepe quickly regains his composure.
Meanwhile, Kragor taps into his ancestral power, muscles tensing with
readiness. Yet danger lurks in the shadows. Suddenly, a crossbow bolt
strikes Doctor Pepe, drawing a pained cry. Another bolt narrowly misses
Halite, while a third strikes him, but only bruises his resilient skin.

Halite spots the assailants: a dwarf and two elves across the pool,
crossbows poised. Outside, Scarlet rushes to Whisper's aid, healing her
with soothing energy. Renewed, Whisper re-enters the cave, her sling
delivering a precise blow to one of the elves before she again retreats
gracefully.

Inside, Doctor Pepe, undeterred by pain, fires back with his crossbow
but misses. Halite steps forward, throwing a javelin that fells the
injured elf with precision. Elara, considering but deciding against
leaping across the pool, channels more divine energy, striking the
second elf squarely. Kragor whispers a curse, dark power seeping from
his words, then unleashes tendrils of energy that knock the elf into the
pool's depths.

Frustrated and fearful, the remaining dwarf curses, raising his crossbow
in desperation. He takes aim at Elara, embedding a bolt into her thigh.
She gasps, momentarily swaying, her focus clouded by the sting.

Retreating further into the cave's depths, the dwarf's footsteps echo
and fade, leaving only the rhythmic drip of water and the murmur of
unseen currents.

\section{Crossing the pool}\label{crossing-the-pool}

Faced with the challenge of pursuing a dwarf across a frigid pool, the
party assesses their options. The wooden beam that seems to have been
used by the bandits sits tantalizingly across the water.

Scarlet throws her grappling hook, but it misses the beam, snagging
something underwater instead. As she pulls, Halite steps in to help.
Together, they haul up a mass: a dead bandit and a distressed, living
frog!

Kragor, sensing danger, hexes the frog and targets it with an eldritch
blast. The frog disintegrates under the force of the blast.

Elara, steadying herself, heals her thigh wound with divine magic.
Scarlet mirrors her, healing Doctor Pepe with nature's energies.

Their reprieve is brief. The dwarf reappears, firing a bolt that bounces
off Halite's armor. ``Damn it,'' Doctor Pepe grumbles, frustration
etched into his features. ``We need to see!'' He hurls his enchanted
dagger, which thuds into the beam, revealing the far shore with its
glow.

Driven by urgency, Whisper leaps onto the wall, climbing swiftly and
landing silently on the far side, her eyes finding the dwarf hidden in
shadows.

With a flick of his wrist, Halite throws the grappling hook, this time
securing the beam. He pulls it towards him until it rests securely
across the pool, then charges confidently across, joining Whisper.
Kragor and the rest of the party follow, anticipation fueling each
stride.

Scarlet conjures a flame to illuminate their path. Doctor Pepe retrieves
his glowing dagger, its light warding off the gloom, as he brings up the
rear.

Seeing them approach, the dwarf panics, firing wildly. The bolt clatters
harmlessly off stone.

\section{Interrogation in the Depths}\label{interrogation-in-the-depths}

In the dim cave light, Whisper, poised and predatory, lunges at the
dwarf, her speed a shadowy blur. Yet the dwarf's shield deflects her
strike with a resonant thud that shakes the cavern. Halite follows
swiftly, his javelin piercing the dwarf with deadly precision, bringing
him to his knees.

Elara arrives, agile and commanding, her voice sharp with authority.
``Tell us the secrets of this place.''

Despite his pain, the dwarf's eyes remain dull and silent. Kragor steps
forward, his voice echoing with Elara's urgency. ``When a lady speaks,
you damn well better listen.''

``What family are you with?'' Halite's voice booms.

``The Uttolot family,'' the dwarf finally admits, defiance lacing his
words.

Halite's massive frame looms over him. ``And what are you doing in this
cave?''

The dwarf swallows hard. ``We\ldots{} we feed the frogs,'' the dwarf
confesses. ``I work here. For Hulil. Train them to carry us. They used
to eat more--- whatever Hulil wanted.''

Scarlet's eyebrow arches. ``More what?'' The dwarf squirms. ``Bats,
small game, even people. Hulil trained them.''

Halite's gaze darkens. ``Tell us about Hulil.'' The dwarf blanches.
``She's sick. Sent several of us to town for a clue to the disease---
but none returned. She plans to sell Tulgi's loot in Shadycreek Run.
Hoping for a cure.''

Whisper leans in. ``Are there traps here? Tell us what you know.''

The dwarf nods toward the sleeping quarters. ``A pit, covered by a
bedroll.''

Halite growls, ``You'll live. For now.'' The dwarf's resigned eyes hint
at fear of what's to come.

Doctor Pepe notices a bucket\ldots{} on closer examination, it is full
of dead bats. ``Interesting. These bats could distract the frogs--- a
tactical edge.''

Doctor Pepe binds the dwarf with rope from his pack. Halite stands
guard, an imposing sentinel.

The others turn their attention to the grim task of searching their
fallen adversaries. Kragor retrieves a crossbow. ``Still serviceable,''
he notes.

Scarlet counts out coins from a waterlogged purse. ``Seven gold, ten
silver,'' she reports, the metal catching the dim light with a dull
gleam. ``Not exactly a king's ransom.''

\section{Dungeon crawl}\label{dungeon-crawl}

In the cave, the prisoner shuffles under Halite's stern watch, boots
scraping the stone floor. They reach a makeshift camp, a fire pit in the
center. Whisper conjures a flame with a soft ``Lux naturae,''
illuminating the scene.

Doctor Pepe's keen eyes catch a bedroll lying suspiciously flat. ``It's
the pit trap of which the dwarf spoke,'' he warns, pointing to the
hidden danger.

Scarlet uncovers an unopened bottle amongst the camp supplies. ``Bald
Dwarf whiskey,'' she notes, smirking. ``Made by elves.''

``Elves making dwarf whiskey? A fine tale,'' Kragor chuckles.

``Nice. That might fetch as much as 25 gold pieces,'' Doctor Pepe notes,
his rogue's mind already calculating potential value.

The party's attention shifts to two corridors leading away from the
campsite. Halite suggests exploring one, with Doctor Pepe following. The
corridor gradually widens, opening into a larger cavern. As their eyes
adjust to the dim light, they realize they are surrounded by hanging
bats.

Suddenly, the bats stir. Their collective movement creates a rustle of
wings that fills the cavern with an ominous sound. Halite, startled,
begins stabbing wildly with his trident. The weapon misses the bats
entirely, instead striking a nearby stalagmite with a sharp crack.

``We need to go!'' Doctor Pepe insists.

The two of them retreat, joining the others who are exploring the second
corridor. ``Bats,'' Halite explains simply.

\section{Old Croaker}\label{old-croaker}

Kragor is the first to notice the expansive underground pool, its dark
waters stretching beyond the reach of their light. The cavern seems to
breathe with subterranean stillness, broken only by the occasional drip
of water from unseen stalactites.

``What's across there?'' Kragor demands, turning to the wounded dwarf.
``How do we get over?''

The dwarf's eyes dart nervously across the water. ``Well,'' he says, his
voice trembling slightly, ``Old Croaker ferries people across.''

Before anyone can ask who or what Old Croaker is, a massive shape begins
to emerge from the murky depths. Even among giant frogs, this creature
is truly enormous--- easily the size of a small boat, its skin a mottled
green and blue, eyes like dark pools of ancient malevolence.

Scarlet steps forward, her movements calm and deliberate. In her hand,
she holds one of the dead bats from their earlier discovery. ``Easy
now,'' she murmurs, her voice a soothing melody of nature's own
language.

With extraordinary skill, Scarlet reaches out with her hand, gently
stroking its massive head. To everyone's amazement, the creature seems
to relax under her touch, its previous menace transforming into
something almost docile. ``We need to cross,'' she tells it softly. Old
Croaker, understanding, moves to the pool's edge.

``Well,'' Elara says, stepping forward with a mixture of excitement and
trepidation, ``I'll go first.'' She carefully climbs onto the frog's
broad back, her movements careful but confident. Old Croaker begins to
swim across the underground pool, Elara perched atop it like an unlikely
queen of this subterranean realm.

\section{Tiamat's priestess}\label{tiamats-priestess}

Elara clings to Old Croaker's back as they glide across the underground
pool. Dismounting with practiced grace, her sharp eyes survey the
cavern. An enormous fire illuminates a scene of unsettling
drama---shadows dance across stone, cast by two robed figures kneeling
before a tapestry depicting a fearsome multi-headed dragon.

The robes of the dwarf woman and the male elf match the tapestry's hues.
The dwarf's blued skin betrays the creeping freezing disease.

Pressing against the cavern wall, Elara watches as Old Croaker swims
back for her companions: Halite, Doctor Pepe, Kragor, and Scarlet.
Whisper stays behind, guarding their captured dwarf informant.

When the party finally joins Elara on the far shore, Scarlet studies the
tapestry with a scholar's precision. ``Tiamat,'' she murmurs, more to
herself than to her companions. ``The scaled tyrant. Embodiment of
greed. One of the betrayer gods, sworn enemy of Bahamut, the Platinum
Dragon.''

``A betrayer god?!,'' exclaims Elara.

Startled, the robed figures turn. Their fire-cast shadows loom
monstrously. The dwarf is unmistakably Hulil Lutan, Tiamat's priestess.

``Halt!'' Hulil barks, her voice crackling with authority. Her diseased
skin gleams with those telltale blue streaks. ``Who dares approach our
sacred space? Drop your weapons and explain yourselves!''

Elara steps forward, her diplomatic mask sliding into place. ``We are
sent by the dragons,'' she says smoothly, ``to understand the origin of
this disease.''

Elara's deception falls flat, and Hulil lets out a sharp, mirthless
laugh. ``Lies! You're nothing but intruders!''

Kragor responds, a sickening glow crackling as he hexes the elf. From
his outstretched hand a purple shock of darkness blasts forward but
misses and strikes stone harmlessly.

Scarlet charges, swinging her quarterstaff fueled by druidic power, but
misses the elf by inches. On the other hand, Doctor Pepe's crossbow bolt
finds the elf's neck, silencing him forever.

Halite throws his javelin with horrifying force and it pierces Hulil's
hip, pain twisting her features. ``Flee!'' she commands in response,
magical compulsion threading her words. But Halite's will remains
unbroken.

A spectral sword materializes, its pommel shaped like a dragon's claw.
It swings at Halite, missing him by a hairsbreadth.

Elara's shortbow sings, her arrow finding Hulil's shoulder. The dwarf
winces but remains standing.

Kragor now turns his hex on Hulil, firing another eldritch blast that
goes wildly off-target.

Doctor Pepe's next shot is solid, sinking deep into Hulil's shoulder and
driving her back momentarily.

Hulil's hand summons a sickly green, jagged blade. She swings it at
Halite, but his armor deflects the strike. Then, with practiced motion,
she pulls out a potion and drinks. Instantly, her wounds begin to heal.

In the dimly lit cavern, Elara's fingers dance over her shimmering harp.
Hulil pauses as the chilling notes paint vivid fears across her mind,
yet, fortified by sheer willpower, she resists the full force of the
arcane assault.

With a gesture imbued with ancient malevolence, Kragor again unleashes
his eldritch blast, a tendril of otherworldly light that tears through
the fabric of reality, wrapped in the chill embrace of necrotic
energies. This time the blast impacts Hulil, and it seethes with the
whispers of forgotten realms, unraveling her very essence beneath a
suffocating miasma of decay. The force spreads like a dark plague,
methodically consuming vitality and sowing despair in its wake, leaving
naught but a hollow echo of cosmic dread.

Allowing no time for Hulil to recover, Scarlet channels natural energy
through her quarterstaff, its wood shimmering with an ethereal glow. As
the staff connects with the Hulil's jaw, Scarlet's druidic power
amplifies the force of the strike, delivering a bone-jarring impact that
crackles with mystical energy.

Hulil staggers to her feet, fury and agony blazing in her eyes like twin
infernos. Doctor Pepe, with ice-cold precision, discharges another bolt,
tearing into the dwarf priestess's abdomen.

Nearby, Halite hears a splash behind him but remains steadfast. With a
swift motion, he plunges his javelin into Hulil's heart. Her eyes wide,
the fire within them slowly extinguishing as she collapses, she rasps a
final curse: ``May you be consumed by endless desire\ldots{} let your
victories sow only tyranny and ruin\ldots{} may all\ldots{} you
covet\ldots{} turn to ash in your grasp.''

\section{Beast gonna feast}\label{beast-gonna-feast}

Meanwhile, hearing the sounds of battle echoing across the cavern,
Whisper knocks out the bound dwarf. Determined to join the fray, she
attempts to scamper across the cave wall. Instead, she slips and falls
with a splash into the water.

Old Croaker startles at the sudden disturbance. The massive frog's head
snaps toward Whisper, jaws wide, but miraculously misses. Whisper swims
away from the predatory amphibian and begins climbing the wall again.

Old Croaker leaps at Whisper but cannot quite reach her, its massive
form creating waves in the underground pool.

Elara attempts to calm the massive frog. ``O magnificent amphibian, if
you take us back across,'' she offers, ``we'll give you more food.'' But
Old Croaker has other ideas. ``Kitten sandwich,'' the frog seems to
communicate, eyeing Whisper with hungry intent.

Kragor hexes the frog and attempts to blast it with eldritch energy.
``Damn it!'' he curses as the blast goes wide.

Doctor Pepe also shoots wildly into the darkness, his bolt disappearing
without effect.

``Who needs enemies with friends like these,'' Elara sighs.

Whisper manages to scramble away into the main cavern, and drops to the
floor. ``Fucking frog!'' she mutters.

Halite surveys the aftermath of battle, a grim idea forming. With raw,
brutal strength, he reaches down to the fallen elf and--- with a
sickening tear--- removes a hand from the corpse. He tosses it to Elara,
who catches it with a mixture of horror and fascination.

Old Croaker lurches toward Elara, its massive form seeking a meal. The
frog's jaws snap, but miraculously miss her. Elara, her stomach turning,
holds out the elf's hand. The massive amphibian sits back, mouth opening
like an oversized baby bird expecting a treat.

``Lovely,'' she mutters. She tosses the hand into the frog's waiting
maw. Old Croaker catches it with frightening efficiency, then silently
slips back into the pool, leaving nothing but ripples in its wake.

\section{What lies within}\label{what-lies-within}

The party scans the room. Beyond the bodies and the imposing altar, a
single chest sits conspicuously against the cavern wall. The massive
Tiamat tapestry looms overhead, its multi-headed dragon seeming to watch
their every move.

A quick search of the bodies yields eight gold pieces and five silver
pieces, but no keys.

Doctor Pepe approaches the chest, his rogue's eye immediately drawn to
its unusual lock. Shaped like a dragon's head, the lock bristles with
intrigue. Small pin holes pepper its surface, each filled with a fine
blue powder. ``Interesting,'' he mutters, carefully examining the
mechanism.

Using a leather pouch to protect his hand, he begins to extract the blue
powder. It's abundant, but his practiced fingers manage to contain most
of it within the pouch.

Scarlet steps forward to examine the chest. She closes her eyes and
murmurs, ``Revela nocuit et morbus.'' As the words weave through the
air, a soft luminous aura emanates from her hands, casting an ethereal
glow.

``There's magical contagion in the pouch,'' she warns. ``And in the
chest itself.'' She pauses, her gaze shifting. ``Oh, and Old Croaker?
Definitely venomous.''

Working together with Elara, Doctor Pepe carefully picks the lock. The
chest opens with a soft click, revealing its treasures: a gilded scroll
case, a jade statuette of a storm giant, a quiver with six clearly
magical arrows, a silver ring set with a jasper stone, 800--900 coins,
and an old notebook.

``These,'' Doctor Pepe says, ``match the items on Urgon's receipt.
Except the two blue vials are missing.''

Doctor Pepe beckons the others closer. With meticulous care, he removes
the chest's contents, ensuring no blue powder is disturbed. He begins to
count the coins, his fingers moving methodically. ``Let's see,'' he
mutters. ``415 copper pieces, 234 silver pieces, 43 electrum pieces, and
112 gold pieces.''

Halite takes the notebook, his massive hands carefully turning the
pages. His eyes narrow as he reads Hulil's journal. ``This is
interesting,'' he says. ``Hulil was trying to collect funds to purchase
a cure for her disease. She sold one of the blue vials to someone named
Irven Liel.''

The party exchanges knowing glances, the weight of their discovery
hanging in the air like a promise of deeper mysteries yet to be
unraveled.

With nothing more to explore, and exhausted from the morning's events,
they decide to leave. They coax Old Croaker once more with bat treats,
using the massive frog to ferry them back across the underground pool.
Retracing their steps, they exit the cavern.

As they step outside, they find the sun high in the sky, its warm light
a stark contrast to the damp, dark world they've just left behind.

Whisper looks back at the cave entrance. ``Fucking frog,'' she mutters
under her breath.

\chapter{Party Inventory}\label{party-inventory}

\begin{DndTable}[header=Currency]{rX}
\textbf{Count} & \textbf{Coin} \\
156 & gold pieces \\
43 & electrum pieces \\
249 & silver pieces \\
415 & copper pieces
\end{DndTable}

\begin{DndTable}[header=Equipment]{rX}
\textbf{Count} & \textbf{Item} \\
1 & Aeorian Dagger \\
1 & Bottle of Bald Dwarf \\
1 & Gilded Scroll Case \\
1 & Jade Statuette of a Storm Giant \\
1 & Silver Ring \\
1 & Hulil’s Journal \\
6 & Arrows +1 \\
1 & grappling hook \\
6 & crossbows \\
30 & bolts \\
5 & scimitars
\end{DndTable}

\DndItemHeader{Arrows, +1}{Weapon, uncommon}

You have a +1 bonus to attack and damage rolls made with this piece of
magic ammunition. Once it hits a target, the ammunition is no longer
magical.

\DndItemHeader{Aeorian Dagger}{Weapon}

A finely wrought dagger previously sold to Pelc's Curiosities, pilfered
by Tulgi Lutan, and surrendered by same to Kragor Grimstride.

\DndItemHeader{Bald Dwarf Whisky}{Consumable, uncommon}

An Uthodurnian specialty spirit, with an estimated value of 25 gp.

\DndItemHeader{Gilded Scroll Case}{Gear}

A finely crafted mahogany container adorned with gold filigree and
inlaid gemstones, providing both beauty and protection for the scrolls
inside. It features runes that offer magical safeguarding against
damage, making it ideal for keeping valuable parchments secure.

\DndItemHeader{Jade Statuette of a Storm Giant}{Miscellaneous}

A meticulously carved figurine, standing approximately eight inches
tall, depicting a storm giant in mid-roar, with intricate details
capturing the raw power and majesty of its kind. The deep green jade
shimmers with veins of gold, suggesting latent magical energies, and
when held during a lightning storm, the statuette seems to vibrate
softly, as if resonating with the storm's fury. Ancient runes inscribed
at the base suggest it could be used in rituals to commune with primal
forces of nature, potentially granting temporary insight or power
related to storms.

\DndItemHeader{Silver Ring}{Jewelry}

A silver ring with an inset jasper stone.

\DndItemHeader{Hulil’s Journal}{Book, common}

Hulil Lutan's journal, mentioning that she sold a vial of blue powder to
Irven Liel.

\chapter{Appendix B --- Dramatis
Personae}\label{appendix-b-dramatis-personae}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Adventurers}: The primary group consisting of Elara, Halite,
  Kragor, Scarlet, Whisper, and Doctor Pepe. Brought together by the
  shared quest to unravel the mystery of a curse tied to Aeorian
  artifacts.
\item
  \textbf{Bandits (Pelc's Curiosities)}: Followers of Hulil, breaking
  into Pelc's Curiosities searching for clues about the curse. They
  engage with the adventurers in combat but surrender after defeat.
\item
  \textbf{Bandits (Croaker Cave)}: Another group working under Hulil,
  tasked with defending the cave. They confront the adventurers as they
  delve deeper into the cave's secrets.
\item
  \textbf{Bill}: A Glassblade, providing warnings at the tavern about
  the dangers associated with the curse impacting Urgon and Tulgi.
\item
  \textbf{Bortock}: A jovial dwarf who tends bar in the local tavern and
  interacts with the adventurers, providing them with refreshments and
  useful local insights.
\item
  \textbf{Doctor Pepe}: Originally a rogue observing the adventurers
  stealthily, he reveals his true intent and aligns with them,
  contributing with his investigative prowess.
\item
  \textbf{Elara}: An aasimar bard whose musical talents and spellcasting
  abilities support and enhance the party's efforts in healing and
  strategic planning.
\item
  \textbf{Elro}: A Glassblade leader who introduces the adventurers to
  the cursed mysteries of Palebank Village, enlisting their help to find
  the root cause.
\item
  \textbf{Gramini}: An elderly elf woman trading potions at the village
  docks, her wares and tales offer resources and clues to the
  adventurers.
\item
  \textbf{Halite}: The goliath fighter wielding a mighty trident, known
  for his strength and tactical astuteness during encounters, especially
  in Croaker Cave.
\item
  \textbf{Hulil Lutan}: The dwarf priestess of Tiamat involved in the
  curse's mystery. She commands operations and holds stolen artifacts at
  Croaker Cave, seeking a cure for her ailment.
\item
  \textbf{Jarl Stonebeard}: The seasoned captain of the
  \emph{Frostwind}, who ferries the adventurers through dangerous seas
  to Palebank Village.
\item
  \textbf{Kragor}: An orc warlock, casting dark magic to strategically
  aid his allies and subdue enemies using curses and powerful eldritch
  blasts.
\item
  \textbf{Old Croaker}: A massive ice frog inhabiting Croaker Cave, it
  aids the adventurers across a subterranean pool, motivated by treats
  provided by Scarlet.
\item
  \textbf{Scarlet}: A druid attuned to nature's magic. She protects and
  guides her comrades using her connection to the natural world and
  magical arts.
\item
  \textbf{Tulgi Lutan}: A solitary trapper cursed with the same
  affliction as Urgon. She's entangled in the theft of Aeorian treasures
  amidst her ties to a Shadycreek Run syndicate.
\item
  \textbf{Urgon}: A dwarven adventurer whose return from Eiselcross with
  treasures and subsequent icy demise sparks the central mystery of the
  story.
\item
  \textbf{Verla Pelc}: The owner of Pelc's Curiosities, found frozen
  lifeless in her shop by the adventurers, indicating the curse's lethal
  reach.
\item
  \textbf{Whisper}: A tabaxi with exceptional agility and stealth, she
  often takes on scouting roles, using her skills to navigate tense
  situations and inform party strategy.
\end{enumerate}

\end{document}
