% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,twoside,twocolumn,openany,nodeprecatedcode]{dndbook}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
%% Build using the D&D template: /nix/store/1sgzm45331wgmchfyl1z80rji555bjis-source
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\newfontfamily\gillius{GilliusADFNo2}[NFSSFamily=GilliusADFNoTwo-LF]
\geometry{footskip=40pt}
\sloppy
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\chapter{Dungeons \& Gardens}\label{dungeons-gardens}

\DndDropCapLine{T}{he salt spray stings your faces} as the longship
grinds against the icy pier of Palebank Village. The groan of
splintering ice mixes with the cries of gulls and the shouts of
dockworkers bundled in furs. Palebank Villages greets you with a blast
of frigid air, a stark contrast to the relative warmth of the southern
seas you've left behind. The sky above is a perpetual grey, heavy with
the promise of more snow.

You've endured weeks at sea, braving treacherous currents and icy
squalls aboard the \emph{Frostwind}, a sturdy, if somewhat cramped,
longship captained by the weathered and taciturn Jarl Stonebeard. The
journey itself proved more than just a test of sea legs; it was during
those long, monotonous days and nights that your paths first crossed.
Over shared meals of salted fish and hardtack, huddled around the meager
warmth of the ship's brazier, you discovered a shared purpose beneath
your disparate backgrounds. Perhaps it was a whispered conversation
overheard in the galley, a chance encounter on deck under the pale
moonlight, or a late-night debate in the cramped crew quarters, but you
each realized you were drawn north by the same alluring whispers: the
rediscovery of Aeorian ruins, remnants of a lost civilization swallowed
by the Frostfell. Tales of lost cities and powerful artifacts have
spread like wildfire, carried on the winds and traded in taverns from
the Menagerie Coast to the shores of Wildemount. These stories have
lured explorers, scholars, and fortune-seekers alike to this desolate
land, and fate, or perhaps something more, has brought you together on
this shared voyage.

Palebank Village, a ramshackle collection of wooden buildings huddled
against the harsh landscape, serves as the primary gateway to the frozen
Island of Eiselcross to the North. Here, amidst the bustle of fur
traders, fisherfolk, grizzled explorers, shady mercenaries and hopeful
fortune-seekers, you disembark. The air is thick with anticipation, a
palpable sense of excitement mixed with a healthy dose of apprehension.
The promise of uncovering lost knowledge, powerful magic, and perhaps
even unimaginable wealth hangs heavy in the air, a beacon in this frozen
wilderness. But the frozen shores of Eiselcross hold many secrets, and
the ruins of Aeor are guarded by more than just ice and snow. Ancient
dangers stir beneath the frozen surface, and the secrets you seek may
come at a terrible price. Your journey into the heart of Eiselcross
begins now, the moment your boots touch the frozen ground.

\chapter{Welcome to Palebank Village}\label{welcome-to-palebank-village}

\DndDropCapLine{I}{n the frosty expanse of the} colder reaches of
Wildemount, in the Greying Wildlands south of the Islands of Eiselcross,
lay the haphazard cluster known as Palebank Village. It was a place more
cobbled together than planned, with just over a hundred cabins and
shacks pressed against the northern cliffs that rose a mere fifteen feet
against the lapping rhythms of the icy harbor waves. The docks, busy
with the absence of departing ships, whispered tales of neglect and
wariness.

On this frigid day, the village was subdued, gathered in mournful
procession for the unfortunate Urgon, a dwarven adventurer whose final
journey was to the graveyard west of the harbor. There, encased in a
casket more suitable for a relic than a beloved friend, he lay suspended
in a state of frozen eternity. Villagers whispered tales of his return
from a year-long venture into Eiselcross, burdened with treasures and a
chilling affliction. Despite countless efforts, Urgon could never find
warmth. Eventually, blue streaks marred his pallor, snaking through his
veins, until his entire being succumbed to the grip of frost.

We followed the procession, taking note of the landscape dotted with
quaint inns and supply shops. Amongst the mourners stood a weathered elf
adorned with the insignia of a ``Glassblade''. Introducing himself as
Elro, he shared that the usual voyages to Aeor had ceased; a silent
testament to the mystery shrouding Urgon's demise. Elro sought our help
in unveiling the source of this insidious curse, admitting that Urgon's
home remained unexplored.

Word reached us quickly that another villager named Tulgi was showing
similar symptoms---her fate seemingly entwined with Urgon's.
Fortuitously, their cabins stood in proximity.

\section{Beer with the Locals}\label{beer-with-the-locals}

In the heart of the village, a jovial dwarf Bortock tended bar at the
local tavern. Elara, ever inquisitive, engaged Bortock in conversation
about Urgon's recent exploits. A night's rest was negotiated---two rooms
for eight silver pieces---before being served beer by the bucket and a
meal of squid rolls.

Bill, a stalwart Glassblade at one of the tavern tables, emphasized that
due to the danger of the curse, all boats were being warned off from
Palebank's docks. Meanwhile, we learned Tulgi was a solitary trapper,
her life a mystery to most.

\section{The Cabins of Urgon and
Tulgi}\label{the-cabins-of-urgon-and-tulgi}

With this knowledge, we ventured to Urgon's cabin where another Glass
Blade vigilantly stood post. Halite led us inside, where chaos had left
its mark. The mounted head of a snowy beast with grey horns seemed to
have overseen the search. Books were strewn about, gear tossed aside as
if someone had been desperately seeking something. Scarlet's keen eyes
caught sight of a grappling hook, swiftly claiming it. Meanwhile, with a
sharp mind for details, Halite, discovered a receipt within a book.
Dated two months prior, it recorded the sale of Aeorian items at the
local Pelc's Curiosities for a handsome sum of one thousand gold pieces.
Among the items: a dagger, a scroll case, a jade statue, a quiver of
arrows, a jasper-set silver ring, and two blue glass vials.

Our eyes traced tracks leading to Tulgi Lutan's snow-burdened cabin. The
warmth of a fierce fire belied the untouched exterior and shuttered
windows. Scarlet's knock brought a curt response, followed by Elara's
soft words which coaxed the door open. Tulgi's face, marked by the same
blue streaks that had doomed Urgon, was a testament to her shared
affliction. She admitted her illness, confessing she and her sister
Hulil, newcomers from Shady Creek Run, were in league with a crime
syndicate. They had been sent to pilfer Aeorian treasures. It was they
who had ransacked Urgon's home, and Tulgi who now surrendered a finely
wrought dagger into Kragor's keeping.

She said that her sister Hulil held the remainder of the treasures in
Croaker Cave, though Tulgi hadn't seen her in weeks.

\section{Onward}\label{onward}

With our next destination clear, we hiked to Pelc's Curiosities. We
found the shop marked by a dragon-gilded ``P'' where the front door
sagged invitingly open, beckoning us into the next chapter of this
unfolding tale.

\chapter{Pelc's Curiosities}\label{pelcs-curiosities}

\DndDropCapLine{T}{he party stands outside Pelc’s} Curiosities, the door
slightly ajar. Suspecting intruders, Whisper closes her eyes while
softly purring ``Maior et Fortior''. The air around her shimmers
momentarily as she draws on her inner ki in concentration. She then
peers into the doors and the windows of the building. Despite her
efforts, she cannot make out very much, though she hears enough rustling
to make her hairs bristle. It sounds as though there are several inside
ransacking the place. Scarlet joins Whisper's investigation, attempting
to divine whether the noises might simply be animals, yet she senses no
wildlife inside.

Preparing for potential conflict, Kragor stands up straight and
stretches out his arms as if to grasp a weapon. In a loud yet distant
voice he exclaims ``Malleum Evoco''. Suddenly ethereal shadows stream in
from all directions and coalesce into an obsidian black war hammer with
an angular and brutal head. Its every surface is etched with subtle
twisting runes. Kragor hefts the weapon with both hands, then widens his
stance with feet planted firmly on the ground.

The goliath Halite likewise readies himself, his massive frame towering
above even Kragor. With deliberate, practiced movements, he adjusts his
gleaming bronze shield, its surface etched with intricate clan markings.
In one enormous hand he carefully grips his trident, its three wickedly
barbed prongs designed not just to pierce, but to tear and rend flesh.
The trident promises not just death, but a savage, lingering demise.

\section{Surprise}\label{surprise}

Inside Pelc's Curiosities lie the answers to the freezing curse. Anxious
for action, Elara takes a deep breath, tapping into her well of magic.
Her fingers trace the air, summoning the rhythm of a battle drum. Her
magic ignites, sending an illusory racket echoing from within the shop's
shadowed walls. Startled into silence, the adversaries within hold their
breath, their schemes momentarily unraveled. As Whisper crouches beside
her, he senses the tension mounting. Without warning, a crossbow bolt
whistles past, narrowly missing him. Elara's calculated ruse works,
urging their foes to react blindly. The door slams shut, a temporary
barrier between them and danger.

``So much for the element of surprise,'' mutters Kragor.

Undeterred, Elara shoulders the door open again. Darkness seeped around
her like ink in water, yet her keen eyes, accustomed to shadow,
discerned the outlines of two startled bandits amid the cluttered ruins
of the shop. Ancient relics lay strewn about like casualties of an
invisible war; toppled bookshelves and shattered relics spoke of a
hasty, chaotic search.

The bandits, their nerves frayed by Elara's eerie magic, released their
crossbow bolts in a jittery frenzy. The bolts missed their marks,
striking harmlessly against worn brick and aged wood. Assessing the
chaotic tableau before her, Elara hesitated; caution whispered in her
ear, suggesting a withdrawal from direct assault into strategic retreat.

\section{Inspiration and Fog}\label{inspiration-and-fog}

She retreated to her waiting comrades, her mind spinning a fresh
tapestry of strategy. Checking again her surroundings, Kragor meets her
gaze with a blend of curiosity and gruff admiration. Her eyes locked
with his, and in that silent exchange, understanding was born. Elara
struck her hand drum, each beat a pulse of power transmitted through the
air, wrapping around Kragor like a cloak of inspiration. The rhythmic
symphony reignited his focus, sharpening his spirit for the clash ahead.

But as this is happening, Scarlet quickly reacts. ``Voco Nubes!'' she
bellows while raising her gnarled staff to the sky. Her eyes close in
concentration as she summons nature's veil. Wisps of mist curl around
her fingers before surging toward the building. The vapor seeps through
cracks and under doorways, expanding rapidly into a dense, swirling fog
that blankets the room. The once-clear space becomes an opaque, ethereal
haze, obscuring vision and muffling sound. The druid smiles, knowing the
shrouded interior will confound any occupants, granting her allies the
advantage they seek within the murky cover of the fog cloud. She wastes
no time taking advantage of it herself: she sneaks into the building and
hugs the wall, moving to the right. She can hear others moving inside as
well, but can make out nothing through the fog.

\section{First Blood}\label{first-blood}

Watching one of his allies attacked and another diving into the fog and
what must certainly be mortal danger, Kragor strains to think. He feels
like a sitting duck outside with obscured enemies inside, ready to make
a pincushion out of him with their crossbow bolts. Taking a deep breath
to overcome his fear, he too rushes through the doorway into the
shrouding fog, gripping his massive conjured war hammer tightly. Unable
to see, he positions himself protectively before where he believes
Scarlet to be, straining to detect any threats hidden in the mist. A
sudden noise to his left spurs him into action. He swings wildly, the
war hammer arcing through the air, and feels a heavy impact followed by
a muffled crunch. The enemy's body collapses to the ground with a
lifeless thud.

\section{The Roof}\label{the-roof}

Outside, Whisper's sharp tabaxi senses are attuned to every movement
around her. As her gaze sweeps upward, it catches upon an unexpected
anomaly: a crouched form perched on the rooftop. Though the figure's
features are obscured by distance, their posture is a tapestry of
uncertainty, a riddle waiting to be unraveled. Without hesitation,
Whisper draws upon her innate agility, launching herself up the
building's facade, her movements a dance of precision and power. Within
moments, she alights upon the roof beside the puzzled figure. As she
closes in, a momentary clumsiness intrudes upon her fluid motion; her
limbs entangle with the figure in a grapple that is awkward but
surprisingly effective. Despite the ungraceful tangle of arms and legs,
her determination holds fast, securing her quarry beneath the vast blue
sky. The figure, now clearly a rogue based on their dark attire and
tools of the trade hanging from their belt, desperately attempts to free
themselves from Whisper's grasp, to no effect.

\section{Counterattack}\label{counterattack}

Halite now grasps the perilous choice the party has made in their
recklessness. With a fierce resolve etched in the hard lines of his
goliath visage, he charges through the fog-choked doorway, instinctively
veering left to secure the flank opposite Scarlet and Kragor. The mist
clings to him, a shroud of uncertainty, yet he moves with the confidence
of one accustomed to the unseen. A bandit lunges at him, the attack a
mere whisper of danger that dissolves into emptiness. Seizing the
opportunity, Halite's fingers tighten around his trident, that harbinger
of despair. With an expert thrust, the weapon slices through the fog,
hungry for blood. It strikes true, embedding itself deep within the
bandit with a sickening resistance, as though the weapon savored its
work. Halite has to struggle to wrench it free from the bandit with raw
power, the action accompanied by a dreadful noise that the fog quickly
absorbs.

While recovering his favored weapon, Halite hears the ``whoosh'' of a
crossbow bolt. He flinches, but he is not the target. He hears Kragor
cry out in desperate pain.

The bolt had struck Kragor just below the collarbone, close to his
heart. Blood flows unchecked, staining his leather armor.

Seconds later, another bolt pierces Scarlet and a sharp pain flares
beneath her ribs. Blood seeps into her cloak, mingling with the forest's
earthy scent.

\section{Rogue Fall}\label{rogue-fall}

Whisper, poised at the edge of the rooftop's precipice, maintains a firm
hold on the rogue. Despite the rogue's cunning and agility, he struggles
to free an arm to launch a counterattack with his dagger. Nevertheless,
Whisper's sharp claws and expert grip keep him securely restrained.
Beneath her, the store's chaos swirls, a symphony of survival and
sorcery; each cry, each clash a note struck sharp in the chord of battle
below. Her decision solidifies with the clarity of ice forming,
abandoning subtlety for swiftness. With a sudden, fluid ferocity, she
thrusts the entangled rogue from the roof, the figure plummeting and
landing with a sickening thud upon the hard earth. The world contracts
around her as she vaults down, feline grace reclaiming momentum in
mid-air, her heart a steady drumbeat beneath her silken fur. She lands
silently, flowing through the doorway like a stream of midnight water
into the tempest of friend and foe, ready once more to thread her
prowess into the weaving of combat's fierce tapestry. The thrown rogue,
battered and broken, lies forgotten amidst the rubble.

Elara is startled by Whisper's sudden reappearance. Despite this, she
remains focused on the building, her senses registering enough to grasp
that her companions are in grave danger. She urgently calls out to
Scarlet, telling her to dispel the fog cloud, which Scarlet promptly
does. Without hesitation, Elara rushes to join her and Kragor inside.
Whisper follows but pauses in the doorway, alert for threats inside or
out.

\section{Medic!}\label{medic}

Surveying Scarlet and Kragor's injuries, she quickly assesses that
Kragor's condition is more critical. She places her hands gently on the
grievous puncture wound left by the crossbow bolt, her touch glowing
with divine energy. The healing light rapidly closes the wound,
restoring vitality to his mottled green-gray skin. Kragor, caught off
guard yet deeply appreciative, meets Elara's kind gaze, and a silent
bond is forged between the orc and the aasimar.

\section{Final Blows}\label{final-blows}

As Elara is tending to Kragor, Scarlet runs towards a nearby bandit that
is just now orienting themselves after the fog dispersed. Eyes glowing
with untamed magic, Scarlet calls upon nature's wrath. With a fierce,
primal incantation, her fingertips elongate into razor-sharp claws,
dripping with corrosive acid. In a swift motion, she lashes out, and her
savage strike lands true. The bandit staggers back, pain etched across
their face as the toxic claws rend through leather and flesh, leaving a
searing wound. The druid's usually gentle demeanor is momentarily
overshadowed by raw, feral power, as the bandit teeters on the brink of
defeat, humbled by nature's unforgiving might.

Halite steps forward with a grim determination, his massive form casting
a foreboding shadow over the bandit struggling to stay upright from
Scarlet's fierce attack. With a swift and fluid motion defying his
immense size, Halite shifts his weight back, then lunges forward with an
uppercut trajectory. It pierces through the air with a whistling sound,
meeting the bandit's chest in a visceral collision. The force of the jab
lifts the bandit off his feet momentarily, his final gasp cut short by
the weapon's deadly embrace. Life flickers out of his eyes, and the limp
body slides down the trident's length. Halite grimaces, more out of
reflex than malice, as he shakes the bandit free with a swift, practiced
motion, the lifeless form dropping to the ground with a thud.

Now sufficiently recovered to rejoin the battle, Kragor focuses his
attention on the bandit far across the room that he suspects of shooting
him. Although he can't be sure of the bandit's guilt, he raises his war
hammer toward his target and shouts, ``Te Exsecro!'' The air shimmers
with malevolent energy as a cold, dark aura coils around the bandit like
an invisible serpent. Without hesitation, Kragor follows with another
spell, yelling ``Dolor,'' and unleashes a surge of eldritch energy from
his war hammer that strikes the bandit square in the chest. The impact
of the blast results in an ugly wound. Immediately, shadowy tendrils
twist and curl over the shredded flesh causing it to blacken and
crumble, leaving the bandit teetering on the brink of death.

\section{Surrender}\label{surrender}

Halite, his towering form casting an imposing shadow across the
cluttered interior of the ransacked antique shop, moved with purpose
toward Kragor's target: a bandit whose bravado had been seared away by
the crackling energy of the orc warlock's magic. The air still shimmered
with the fading traces of arcane power, and the bandit, already on the
brink of collapse, could only watch as the goliath fighter closed the
distance between them like an inexorable force of nature.

The trident in Halite's grip gleamed with an unsettling menace, its
barbed points promising a swift and painful end should it be called upon
to deliver one. The bandit, a mere lithe elf in the presence of such
formidable warriors, felt the weight of his own mortality for what
seemed like the first time. His sword clattered to the wooden floor, a
hollow sound that resonated through the shop, punctuating his surrender.

``I yield,'' the bandit croaked, his voice strained with fear and
desperation. He raised his hands, palms open and empty, a universal sign
of capitulation. His eyes darted to his remaining comrade, wide with
silent urging.

The last standing bandit, who had watched the battle unfold with growing
dread, knew the odds all too well. He had witnessed the fate of their
fallen companions---three already dispatched with ruthless efficiency by
the duo of Kragor and Halite. The decision was not a difficult one.

He dropped his own weapon, a well-worn crossbow, to the floor and raised
his hands above his head in submission. ``We don't want anymore
trouble,'' he said, his voice carrying a tremor that matched the frantic
beating of his heart.

Kragor surveyed the scene, his eyes, glowing faintly with residual
magical energy, meeting Halite's. An unspoken understanding passed
between them---this victory, as hard-fought as it was, did not need to
claim further lives.

With the tension of combat beginning to ebb, the antique shop's air felt
still, though the echoes of the skirmish lingered. Surrounded by
overturned furniture and scattered relics of a bygone era, the bandits'
surrender marked the end of the struggle, their lives spared by the
mercy of those far mightier than they.

Whisper, having ensured the rogue she tossed from the roof was no longer
a threat, finally entered the antique shop and closed the door behind
her. As she did, the rogue moved to a crouched position around the
corner, relieved that his theatrics had been successful. Intending to
enter the building when the coast was truly clear, he remained vigilant,
pressing his ear to the cool glass of the window to eavesdrop on the
victorious adventurers.

\section{Interrogation}\label{interrogation}

Elara and Scarlet eyed the bandits with intensity, their curiosity
piqued by the confession of surrender. ``Who are you and what were you
doing here?'' Elara demanded, her voice steady yet demanding answers.

The first bandit, regaining a bit of composure but still visibly shaken,
replied, ``We were sent by Hulil, a priestess of Tiamat. She instructed
us to search this place. Two months ago, there was a robbery here, and
now Hulil's got this strange freezing sickness. She hoped we might find
a clue here in the shop. But we found nothing.''

Scarlet's gaze remained firm as she pressed further, ``Then why did you
attack us?''

A hint of embarrassment colored the bandit's cheeks. ``We were spooked.
We heard some weird noise, then you guys barged in. Especially that
chick with a horn on her head,'' he gestured toward Elara. ``We
panicked. We're not used to dealing with people like you.''

In the meantime, the rogue outside, crouching below the window, absorbed
the exchange, piecing together the dynamics at play.

Scarlet produced a weathered receipt with notations about Aeorian
artifacts and presented it to the bandits. ``Have you seen these
items?''

``They're with Hulil,'' the bandit admitted reluctantly, his eyes on the
documentation with evident recognition. ``She's at Croaker's Cave,''
confirming what the party had already learned from Hulil's sister,
Tulgi.

Satisfied with the information, Kragor dismissed the subdued bandits in
no uncertain terms: ``Leave everything and get out.'' Seizing their
chance, the bandits quickly discarded their weapons and coins before
hurrying for the door, the rogue outside remaining concealed until the
coast was truly clear.

\section{Loot}\label{loot}

After searching the bandits' leavings and their late compatriots'
bodies, the party tallied the loot: 14 gold pieces, eight silver pieces,
five crossbows, 30 bolts, five scimitars, and a dwarf-sized shirt
blazoned with ``Scanlan Shorthalt --- The Meat Man Cometh''. (Elara
judged this last item to be a rare find and might fetch as much as two
gold pieces.)

The party then turned to the antique shop, assessing the chaos that
engulfed it. The room was in disarray, bookshelves overturned and
trinkets strewn about. Amidst the disorder, they stumbled upon a
chilling sight---a frozen elf lying lifeless in bed. It was Verla Pelc,
and the grim discovery confirmed that the place had not seen tidiness
for weeks.

In a thorough inspection of both the shop and the dead bandits'
belongings, they discovered two bows and various odds and ends. Deciding
a respite was in order, they planned to rest before heading to Croaker
Cave.

\section{Who is this guy?}\label{who-is-this-guy}

Unbeknownst to the adventurers, the rogue remained vigilant, listening
to their intentions and preparing to bide his time until they left.

\chapter{Party Inventory}\label{party-inventory}

\begin{DndTable}[header=Currency]{rX}
\textbf{Count} & \textbf{Coin} \\
14 & gold pieces \\
8 & silver pieces
\end{DndTable}

\begin{DndTable}[header=Equipment]{rX}
\textbf{Count} & \textbf{Item} \\
1 & Aeorian(?) Dagger \\
1 & grappling hook \\
5 & crossbows \\
30 & bolts \\
5 & scimitars \\
1 & Shorthalt Concert Shirt
\end{DndTable}

\DndItemHeader{Aeorian(?) Dagger}{Wondrous item, rare}

A finely wrought dagger previously sold to Pelc's Curiosities, pilfered
by Tulgi Lutan, and surrendered by same to Kragor Grimstride.

\DndItemHeader{Shorthalt Concert Shirt}{Wondrous item, rare}

A dwarf-sized shirt blazoned with ``Scanlan Shorthalt --- The Meat Man
Cometh''.

Value: two gold pieces.

\chapter{Appendix B --- Dramatis
Personae}\label{appendix-b-dramatis-personae}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Bandits}: Guild members working for Hulil, they break into
  Pelc's Curiosities searching for clues about the curse and engage in
  combat with the adventurers before surrendering.
\item
  \textbf{Bill}: A Glassblade seated in the tavern, warning of the
  dangers associated with the curse impacting Urgon and Tulgi.
\item
  \textbf{Bortock}: A jovial dwarf who tends bar in the local tavern,
  interacting with the adventurers and providing them with refreshments
  and lodging information.
\item
  \textbf{Elara}: An inquisitive member of the party, likely with
  magical abilities, as she performs spells and aids Kragor with
  healing.
\item
  \textbf{Elro}: A weathered elf adorned with the insignia of a
  ``Glassblade.'' He introduces himself to the adventurers at Urgon's
  funeral and seeks their help in determining the cause of the curse.
\item
  \textbf{Halite}: A towering goliath fighter, characterized by his
  immense size and strength. His weapon of choice is a massive trident,
  and he acts with determination and strategy during conflicts.
\item
  \textbf{Hulil Lutan}: Tulgi's sister, a priestess of Tiamat, and the
  mastermind behind the search for clues related to the freezing
  sickness. She has the remainder of stolen treasures at Croaker Cave.
\item
  \textbf{Jarl Stonebeard}: The weathered and taciturn captain of the
  longship \emph{Frostwind} that brought the adventurers to Palebank
  Village. His demeanor is quiet, and he is experienced with sailing
  through icy waters.
\item
  \textbf{Kragor}: An orc warlock, wielding dark magic and an ethereal
  war hammer. He's strategically minded and capable of casting eldritch
  spells to protect his allies and subdue enemies.
\item
  \textbf{Rogue}: A thief initially grappled by Whisper on the roof.
  Though he seems defeated, he stealthily listens to the adventurers'
  plans, suggesting future intrigue.
\item
  \textbf{Scarlet}: A druid with access to nature magic, demonstrated by
  her ability to summon mist and turn her fingertips into toxic claws
  during combat.
\item
  \textbf{Tulgi Lutan}: A solitary trapper and one of the afflicted with
  the same symptoms as Urgon. She, along with her sister Hulil, were
  involved in stealing Aeorian treasures as part of a crime syndicate.
\item
  \textbf{Urgon}: A deceased dwarven adventurer who returned from
  Eiselcross with treasures and a chilling affliction. His demise is a
  centerpiece of the story, leading the adventurers to investigate the
  source of his mysterious curse.
\item
  \textbf{Verla Pelc}: The owner of Pelc's Curiosities, discovered
  frozen and lifeless in the shop by the adventurers, indicating the
  seriousness of the ongoing curse.
\item
  \textbf{Whisper}: A tabaxi with sharp senses and agility, capable of
  moving swiftly and silently, proving her skills when grappling with a
  rogue on the rooftop.
\end{enumerate}

\end{document}
